Enhancing Underwater Imagery using Generative Adversarial Networks

### 2017-09-25 files/paper/tex_plain_version/experiments.tex
plain version added

\begin{figure}[th]
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.75cm}}

   ~\quad Original & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\

   \includegraphics[width=0.8in]{n01917289_4982_real} &
   \includegraphics[width=0.8in]{n01917289_4982_gen_0} &
   \includegraphics[width=0.8in]{n01917289_4982_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_16340_real} &
   \includegraphics[width=0.8in]{n01496331_16340_gen_0} &
   \includegraphics[width=0.8in]{n01496331_16340_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_22183_real} &
   \includegraphics[width=0.8in]{n01496331_22183_gen_0} &
   \includegraphics[width=0.8in]{n01496331_22183_gen_1} \\

   \includegraphics[width=0.8in]{n01664065_29738_real} &
   \includegraphics[width=0.8in]{n01664065_29738_gen_0} &
   \includegraphics[width=0.8in]{n01664065_29738_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_11938_real} &
   \includegraphics[width=0.8in]{n01496331_11938_gen_0} &
   \includegraphics[width=0.8in]{n01496331_11938_gen_1} \\

   \includegraphics[width=0.8in]{n02606052_2969_real} &
   \includegraphics[width=0.8in]{n02606052_2969_gen_0} &
   \includegraphics[width=0.8in]{n02606052_2969_gen_1} \\

   \includegraphics[width=0.8in]{n01914609_1607_real} &
   \includegraphics[width=0.8in]{n01914609_1607_gen_0} &
   \includegraphics[width=0.8in]{n01914609_1607_gen_1} \\

   \includegraphics[width=0.8in]{n02607072_6241_real} &
   \includegraphics[width=0.8in]{n02607072_6241_gen_0} &
   \includegraphics[width=0.8in]{n02607072_6241_gen_1} \\

@@

% I would like this table to match up with the figure showing edge detections. I wasn't able to
% get letters on the left side at each row though.
\begin{table}
\centering
\caption{Distances in image space}
\begin{tabular}{| c | c | c | c |}
   \hline
   Row/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   A          & 116.45 & 85.71  & 86.15  \\ \hline
   B          & 114.49 & 97.92  & 101.01 \\ \hline
   C          & 120.84 & 96.53  & 97.57  \\ \hline
   D          & 129.27 & 108.90 & 110.50 \\ \hline
   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
\end{tabular}
\label{tab:one}
\end{table}

%\newpage

% \begin{figure*}[h]
% \centering
% \begin{tabular}{p{.4cm} p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
%   
%    Set & ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
% 
%    \multirow{2}{*}{A} & \includegraphics[width=0.8in]{1_original} &
%    \includegraphics[width=0.8in]{1_cimg} &
%    \includegraphics[width=0.8in]{1_u0img} &
%    \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
%    \includegraphics[width=0.8in]{1_oedges} &
%    \includegraphics[width=0.8in]{1_cedges} &
%    \includegraphics[width=0.8in]{1_u0edges} &
%    \includegraphics[width=0.8in]{1_u1edges} \\
% 
%    \multirow{2}{*}{B} & \includegraphics[width=0.8in]{2_original} &
%    \includegraphics[width=0.8in]{2_cimg} &
%    \includegraphics[width=0.8in]{2_u0img} &
%    \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
%    \includegraphics[width=0.8in]{2_oedges} &
%    \includegraphics[width=0.8in]{2_cedges} &
%    \includegraphics[width=0.8in]{2_u0edges} &
%    \includegraphics[width=0.8in]{2_u1edges} \\
% 
%    \multirow{2}{*}{C} & \includegraphics[width=0.8in]{3_original} &
%    \includegraphics[width=0.8in]{3_cimg} &
%    \includegraphics[width=0.8in]{3_u0img} &
%    \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
%    \includegraphics[width=0.8in]{3_oedges} &
%    \includegraphics[width=0.8in]{3_cedges} &
%    \includegraphics[width=0.8in]{3_u0edges} &
%    \includegraphics[width=0.8in]{3_u1edges} \\
%    
%    \multirow{2}{*}{D} & \includegraphics[width=0.8in]{4_original} &
%    \includegraphics[width=0.8in]{4_cimg} &
%    \includegraphics[width=0.8in]{4_u0img} &
%    \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
%    \includegraphics[width=0.8in]{4_oedges} &
%    \includegraphics[width=0.8in]{4_cedges} &
%    \includegraphics[width=0.8in]{4_u0edges} &
%    \includegraphics[width=0.8in]{4_u1edges} \\
% 
% \end{tabular}
% \caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
% and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
% the result of the edge detector.}
% \label{fig:canny_samples}
% \end{figure*}

\begin{figure}[h]
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.75cm}}

   ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\

   \includegraphics[width=0.8in]{1_original} &
   \includegraphics[width=0.8in]{1_cimg} &
   \includegraphics[width=0.8in]{1_u0img} &
   \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{1_oedges} &
   \includegraphics[width=0.8in]{1_cedges} &
   \includegraphics[width=0.8in]{1_u0edges} &
   \includegraphics[width=0.8in]{1_u1edges} \\

   \includegraphics[width=0.8in]{2_original} &
   \includegraphics[width=0.8in]{2_cimg} &
   \includegraphics[width=0.8in]{2_u0img} &
   \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{2_oedges} &
   \includegraphics[width=0.8in]{2_cedges} &
   \includegraphics[width=0.8in]{2_u0edges} &
   \includegraphics[width=0.8in]{2_u1edges} \\

   \includegraphics[width=0.8in]{3_original} &
   \includegraphics[width=0.8in]{3_cimg} &
   \includegraphics[width=0.8in]{3_u0img} &
   \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{3_oedges} &
   \includegraphics[width=0.8in]{3_cedges} &
   \includegraphics[width=0.8in]{3_u0edges} &
   \includegraphics[width=0.8in]{3_u1edges} \\

   \includegraphics[width=0.8in]{4_original} &
   \includegraphics[width=0.8in]{4_cimg} &
   \includegraphics[width=0.8in]{4_u0img} &
   \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{4_oedges} &
   \includegraphics[width=0.8in]{4_cedges} &
   \includegraphics[width=0.8in]{4_u0edges} &
   \includegraphics[width=0.8in]{4_u1edges} \\

\end{tabular}
\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
the result of the edge detector. The figure depicts four different sets of images, successively labeled A to D from top to 
bottom. See Table~\ref{tab:one}.}
\label{fig:canny_samples}
\vspace{-5mm}
\end{figure}

% TODO definitely need help with formatting, but content is there
\begin{figure*}
\centering
\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}

@@

\begin{figure*}
\begin{tabular}{p{1.8cm} p{1.85cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.9cm} }

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   \multicolumn{1}{|p{.7cm}|}{\centering Method/ \\ Patch} & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\label{fig:gdl_tbl}
\end{table}

\begin{table}[ht]
\footnotesize
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   \multicolumn{1}{|p{.7cm}|}{\centering Method/ \\ Patch} & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ 
\hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\label{fig:mean_tbl}
\end{table}

>>>>

\begin{figure}[!ht]
\centering
\footnotesize
\begin{tabular}{p{1.6cm} p{1.6cm} p{1.6cm}}
   Original & \textbf{UGAN} & \textbf{UGAN-P} \\
   \includegraphics[width=0.7in]{n01917289_4982_real} &
   \includegraphics[width=0.7in]{n01917289_4982_gen_0} &
   \includegraphics[width=0.7in]{n01917289_4982_gen_1} \\

   \includegraphics[width=0.7in]{n01496331_16340_real} &
   \includegraphics[width=0.7in]{n01496331_16340_gen_0} &
   \includegraphics[width=0.7in]{n01496331_16340_gen_1} \\

   \includegraphics[width=0.7in]{n01496331_22183_real} &
   \includegraphics[width=0.7in]{n01496331_22183_gen_0} &
   \includegraphics[width=0.7in]{n01496331_22183_gen_1} \\

   \includegraphics[width=0.7in]{n01664065_29738_real} &
   \includegraphics[width=0.7in]{n01664065_29738_gen_0} &
   \includegraphics[width=0.7in]{n01664065_29738_gen_1} \\

   \includegraphics[width=0.7in]{n01496331_11938_real} &
   \includegraphics[width=0.7in]{n01496331_11938_gen_0} &
   \includegraphics[width=0.7in]{n01496331_11938_gen_1} \\

   \includegraphics[width=0.7in]{n02606052_2969_real} &
   \includegraphics[width=0.7in]{n02606052_2969_gen_0} &
   \includegraphics[width=0.7in]{n02606052_2969_gen_1} \\

   \includegraphics[width=0.7in]{n01914609_1607_real} &
   \includegraphics[width=0.7in]{n01914609_1607_gen_0} &
   \includegraphics[width=0.7in]{n01914609_1607_gen_1} \\

   \includegraphics[width=0.7in]{n02607072_6241_real} &
   \includegraphics[width=0.7in]{n02607072_6241_gen_0} &
   \includegraphics[width=0.7in]{n02607072_6241_gen_1} \\

@@

% I would like this table to match up with the figure showing edge detections. I wasn't able to
% get letters on the left side at each row though.
\begin{table}
\centering
\footnotesize
\caption{Distances in image space}
\begin{tabular}{| c | c | c | c |}
   \hline
   Row/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   A          & 116.45 & 85.71  & 86.15  \\ \hline
   B          & 114.49 & 97.92  & 101.01 \\ \hline
   C          & 120.84 & 96.53  & 97.57  \\ \hline
   D          & 129.27 & 108.90 & 110.50 \\ \hline
   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
\end{tabular}
\label{tab:one}
\end{table}

\begin{figure}[!ht]
\centering
\footnotesize
\begin{tabular}{p{1.6cm} p{1.6cm} p{1.6cm} p{1.6cm}}
   Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\
   \includegraphics[width=0.7in]{1_original} &
   \includegraphics[width=0.7in]{1_cimg} &
   \includegraphics[width=0.7in]{1_u0img} &
   \includegraphics[width=0.7in]{1_u1img} \\ [-1ex]
   \includegraphics[width=0.7in]{1_oedges} &
   \includegraphics[width=0.7in]{1_cedges} &
   \includegraphics[width=0.7in]{1_u0edges} &
   \includegraphics[width=0.7in]{1_u1edges} \\

   \includegraphics[width=0.7in]{2_original} &
   \includegraphics[width=0.7in]{2_cimg} &
   \includegraphics[width=0.7in]{2_u0img} &
   \includegraphics[width=0.7in]{2_u1img} \\ [-1ex]
   \includegraphics[width=0.7in]{2_oedges} &
   \includegraphics[width=0.7in]{2_cedges} &
   \includegraphics[width=0.7in]{2_u0edges} &
   \includegraphics[width=0.7in]{2_u1edges} \\

   \includegraphics[width=0.7in]{3_original} &
   \includegraphics[width=0.7in]{3_cimg} &
   \includegraphics[width=0.7in]{3_u0img} &
   \includegraphics[width=0.7in]{3_u1img} \\ [-1ex]
   \includegraphics[width=0.7in]{3_oedges} &
   \includegraphics[width=0.7in]{3_cedges} &
   \includegraphics[width=0.7in]{3_u0edges} &
   \includegraphics[width=0.7in]{3_u1edges} \\

   \includegraphics[width=0.7in]{4_original} &
   \includegraphics[width=0.7in]{4_cimg} &
   \includegraphics[width=0.7in]{4_u0img} &
   \includegraphics[width=0.7in]{4_u1img} \\ [-1ex]
   \includegraphics[width=0.7in]{4_oedges} &
   \includegraphics[width=0.7in]{4_cedges} &
   \includegraphics[width=0.7in]{4_u0edges} &
   \includegraphics[width=0.7in]{4_u1edges} \\
\end{tabular}
\vspace{-2mm}
\caption{\small{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
the result of the edge detector. The figure depicts four different sets of images, successively labeled A to D from top to 
bottom. See Table~\ref{tab:one}.}}
\label{fig:canny_samples}
\vspace{-5mm}
\end{figure}

% TODO definitely need help with formatting, but content is there
\begin{figure*}[!ht]
\centering
\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}

@@

\begin{figure*}[!ht]
\begin{tabular}{p{1.8cm} p{1.85cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.9cm} }

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   Method/Patch & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\label{fig:gdl_tbl}
\end{table}

\begin{table*}[ht]
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   Method/Patch & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ 
\hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\label{fig:mean_tbl}
\end{table*}
